Social Patriotism

### 2016-02-15 writing_in_ethics/paper_two.tex
algorithm work

\addbibresource{generic_bib.bib}

@@

The third scenario present by the text involves Brandon Mayfield, an attorney from Portland, Oregon. The FBI was presented with a partial fingerprint recovered from a terrorist attack in Spain that was linked back to Mayfield. The FBI then proceeded to investigate Mayfield, going as far as entering his home and seizing private information without proper legal authorization. This scenario differs from others in that the FBI's actions were directly aimed at Mayfield. They did not use anyone as a means to an end, as they did in other scenarios. However, they still violated Kant's Categorical Imperative. Kantianism focuses on the idea that moral laws should be able to be willed into universal laws, and as such, no party involved should be able to opt-out. Following this logic, Mayfield, as well as anyone else who wanted to, would be able to take information without legal basis from the FBI. This scenario differs from the previous two in that the FBI's intention is known. The agency sought to bring a suspected terrorist into custody. The methods used to reach that goal were not ethical however, which makes their actions unethical.

It appears that under Kantian analysis, many of the actions taken by the FBI are unethical. 
\end{linenumbers}
\newpage
\printbibliography
\end{document}

>>>>

\addbibresource{generic_bib.bib}
\addbibresource{paper_two_bib.bib}

@@

The third scenario presented by the text involves Brandon Mayfield, an attorney from Portland, Oregon. The FBI was presented with a partial fingerprint recovered from a terrorist attack in Spain that was linked back to Mayfield. The FBI then proceeded to investigate Mayfield, going as far as entering his home and seizing private information without proper legal authorization. This scenario differs from others in that the FBI's actions were directly aimed at Mayfield. They did not use anyone as a means to an end, as they did in other scenarios. However, they still violated Kant's Categorical Imperative. Kantianism focuses on the idea that moral laws should be able to be willed into universal laws, and as such, no party involved should be able to opt-out. Following this logic, Mayfield, as well as anyone else who wanted to, would be able to take information without legal basis from the FBI. This scenario differs from the previous two in that the FBI's intention is known. The agency sought to bring a suspected terrorist into custody. The methods used to reach that goal were not ethical however, which makes their actions unethical.

It appears that under Kantian analysis, many of the actions taken by the FBI are unethical. The Patriot Act allows for the government to interfere with the lives of the American population with little regard for the law, but the legality of an action does not necessarily determine whether that action is ethically right or wrong.  It is hard to say whether or not the Patriot Act itself is ethical or not, but many of the ways in which law enforcement has interpreted and used it are unethical. 
\end{linenumbers}
\newpage
\nocite{*}
\printbibliography
\end{document}
